The importance of fidelity in the scheduling of Redox Flow Batteries.

### 2018-11-14 Paper/main.tex
Update main.tex

\cref{fig:winter_day_schedules,fig:summer_day_schedules} show the optimal LP and NLP schedules for example winter and summer days from 2017. Although the revenue obtained is \pounds 0.074 for both days under the NLP optimal schedule, the required throughput of the battery is greater on the summer day. This has an impact on the error of the LP revenue estimation - for the winter day the revenue is estimated at \pound 0.088, whereas on the summmer day it is estimated at \pound 0.099. The error in the estimation of revenue under the LP optimisation is dependent on energy throughput.

>>>>

\cref{fig:winter_day_schedules,fig:summer_day_schedules} show the optimal LP and NLP (\cref{Model_Formulation_Constraint_Cell_Voltage}) schedules for example winter and summer days from 2017. Although the revenue obtained is \pounds 0.074 for both days under the NLP optimal schedule, the required throughput of the battery is greater on the summer day. This has an impact on the error of the LP revenue estimation - for the winter day the revenue is estimated at \pound 0.088, whereas on the summmer day it is estimated at \pound 0.099. The error in the estimation of revenue under the LP optimisation is dependent on energy throughput.
